Device fingerprinting for user authentication in web applications \titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}

### 2018-11-08 paper.tex
Add title
Fix typo in abstract

\title{Fingerprinting
\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
%%%  \subtitle{[Extended Abstract]
%%% \titlenote{A full version of this paper is available as
%%% \textit{Author's Guide to Preparing ACM SIG Proceedings Using
%%% \LaTeX$2_\epsilon$\ and BibTeX} at
%%% \texttt{www.acm.org/eaddress.htm}}}

@@

\maketitle
\begin{abstract}
    Device fingerprinting is a modern technique which, instead of using traditional user identifiers (e.g. cookies and local storage), leverages on existing information available from user's device.
    In this paper, we investigates the various state-of-the-art technologies for device fingerprinting and authentification systems that utilize such fingerprint information. We analyzes the trade-off between the uniqueness of the identifer generated and ease of use for authentication. Lastly, we also build a simple authentication system that can be reused and extended in real-world web applications.
\end{abstract}

>>>>

\title{Device fingerprinting for user authentication in web applications
\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
%%%  \subtitle{[Extended Abstract]
%%% \titlenote{A full version of this paper is available as
%%% \textit{Author's Guide to Preparing ACM SIG Proceedings Using
%%% \LaTeX$2_\epsilon$\ and BibTeX} at
%%% \texttt{www.acm.org/eaddress.htm}}}

@@

\maketitle
\begin{abstract}
    Device fingerprinting is a modern technique which, instead of using traditional user identifiers (e.g. cookies and local storage), leverages on existing information available from user's device.
    In this paper, we investigates the various state-of-the-art technologies for device fingerprinting and authentication systems that utilize such fingerprint information. We analyzes the trade-off between the uniqueness of the identifer generated and ease of use for authentication. Lastly, we also build a simple authentication system that can be reused and extended in real-world web applications.
\end{abstract}
